Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-07 ms.tex
putting back Ia h/c

>>>>

If Ia supernovae are the dominant source of heating we expect $\rs\sim
r_{\rm Ia}$. If the stagnation radius moves inwards from $\rIa$, the
decreased heating will force it outwards again. If the it moves
outwards the Ia heating will force it inwards. Thus,
equations~\eqref{eq:cooling2} and ~\eqref{eq:Mdotmax} will no longer
be valid as they assume that $\rs$ follows equation
\eqref{eq:stag_simple}. We derive $\dot{q}_{\rm
  heat}/\left|\dot{q}_{\rm rad}\right|$ for $\rs=\rIa$ to evaluate
thermal stability in SNe Ia dominate the heating.

\begin{align}
&\rho(\rIa)\simeq \frac{3 q(\rIa)}{2-\Gamma} \nonumber\\
&T(\rIa)\simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v^{\rm Ia \,\,
    2}_{w}}{2k}\nonumber\\
&\left.\frac{\dot{q}_{\rm heat}}{\left|\dot{q}_{\rm rad}\right|}\right|_{\rIa}\simeq
\begin{cases}
  90 \Mbheight^{1.3} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{-3}
  \eta_{0.02}^{-2.7} & \text{core}\nonumber\\
   90 \Mbheight^{0.8} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{-2.7}
  \eta_{0.02}^{-2.7} & \text{cusp}\nonumber\\
\end{cases}\\&\simeq
\begin{cases}
  90 \Mbheight^{1.3} (\epsilon_{\rm Ia}/0.4)^{1.7}
  (\tau_{\star}/\th)^{0.5}
 & \text{core}\\
   90 \Mbheight^{0.8} (\epsilon_{\rm Ia}/0.4)^{1.7} (\tau_{\star}/\th)^{0.9}
  & \text{cusp}\\
\end{cases}
\end{align}
